Papers

### 2023-09-23 quarto/index.qmd
update

**Aston Zhang** is a research scientist at Meta Generative AI, building large language models.
Previously, he was a scientist at Amazon Web Services AI Research.
He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
an ACM Ubicomp Distinguished Paper Award, and an ACM SenSys Best Paper Award Nomination.
His <a href="https://github.com/d2l-ai" target="_blank">open-source</a> textbook,
<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>,
has been <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained his Ph.D. in Computer Science from University of Illinois at Urbana-Champaign.

>>>>

**Aston Zhang** is a research scientist at Meta Generative AI, building large language models.
Prior to this, he was a scientist/manager at Amazon Web Services AI Research,
studying language and multimodal models.
He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
an ACM Ubicomp Distinguished Paper Award, and an ACM SenSys Best Paper Award Nomination.
His <a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a> textbook
is <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained a Ph.D. in Computer Scientist from University of Illinois Urbana-Champaign.
